The Influence of Connectivity on Dung Beetle Communities

### 2025-07-05 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
buuuuuuuuu
hummmmm

@@

```{r, label = srs-map, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Experimental block with the different patches and distance between them.", out.width="40%", fig.align='center'}

>>>>

In comparing patc

@@

```{r echo=FALSE, fig.align='center', fig.cap="Experimental block with the different patches and distance between them.", message=FALSE, warning=FALSE, label=srs-map, out.width="40%"}
